analysis-pilot

### 2023-08-01 code/analysis-pilot.Rmd
new
new1

#accuracy graph
```{r}
accuracy <- filtered_data %>% 
  group_by(gameId) %>% 
  summarize(total=n(),
            correct=sum(countCorrect)) %>% 
  mutate(fraction = correct/total*100, percent = signif(fraction, 2))

ggplot(data = accuracy, aes(y = gameId, x = percent)) +
  geom_bar(stat = "identity", position = position_dodge(.9), color = "black", fill = "#228B22", width = .7) +
  geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  theme_classic() +
  xlab("Percentage Accuracy") +
  ylab("Game ID") +
  theme(aspect.ratio = 4/5,
        axis.title = element_text(size=14,face="bold"),
        axis.text = element_text(size=12),
        legend.position = "none")
```

time=time

#graph accuracy to time (scatterplot maybe?)
#graph accuracy (bar graph)

>>>>

#accuracy graph
```{r}
accuracy <- filtered_data %>% 
  group_by(game) %>% 
  summarize(total=n(),
            correct=sum(countCorrect)) %>% 
  mutate(fraction = correct/total*100, percent = signif(fraction, 2))

ggplot(data = accuracy, aes(y = game, x = percent)) +
  geom_bar(stat = "identity", position = position_dodge(.9), color = "black", fill = "#228B22", width = .7) +
  geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  theme_classic() +
  xlab("Percentage Accuracy") +
  ylab("Game ID") +
  theme(aspect.ratio = 4/5,
        axis.title = element_text(size=14,face="bold"),
        axis.text = element_text(size=12),
        legend.position = "none")
```

#graph accuracy to time (scatterplot maybe?)
